\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}	% Para caracteres en español
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{multirow,booktabs}
\usepackage[table]{xcolor}
\usepackage{fullpage}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{calc}
\usepackage{multicol}
\usepackage{cancel}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\newlength{\tabcont}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}
\usepackage{empheq}
\usepackage{framed}
\usepackage[most]{tcolorbox}
\usepackage{xcolor}
\colorlet{shadecolor}{orange!15}
\parindent 0in
\parskip 12pt
\geometry{margin=1in, headsep=0.25in}
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{reg}{Rule}
\newtheorem{exer}{Exercise}
\newtheorem{note}{Note}
\begin{document}
\setcounter{section}{0}
\title{Project Diary of Cookman \& Gadd-Speakman}

\thispagestyle{empty}

\begin{center}
{\LARGE \bf Project Diary of \\
Ben Cookman \& Bradly Gadd-Speakman}\\
{\Large Project 3/4, Department of Mathematical Sciences, Durham University}\\
{\Large 2022-23}
\end{center}
\section{October $5^{\text{th}}$, 2022 - 11:00-11:40}
In this meeting, we reviewed the general plan of the project. We got to know about Brad and Ben's background and interests. We briefly discussed discretisation in time and space and I explained the focus of this project is time integration. I shortly mentioned why parallelisation in time is challenging. Ben and Brad showed interest to pick Julia as the programming language for this project. We decided to use Git/Github as the main platform for sharing files and scripts and collaboration. 
\begin{shaded}
\textbf{Assignment of the week} \newline
Brad and Ben will familiarise themselves with Git/Github, review classical time integrators and write scripts that solve simple ODEs using these integrators. Several sources for numerical ODEs (as well as a package for using Git/Github) were shared with them.
\end{shaded}

\section{October $12^{\text{th}}$, 2022 - 11:00-11:40}

Brad and Ben shared their progress during the last week. They had coded Forward Euler and multi-step time integrators and used them to find the numerical solution of a few ODE examples. We talked about Spectral Deferred Correction method briefly and took a loot at the paper by Dutt et al. (2000). 
\begin{shaded}
\textbf{Assignment of the week} \newline
Brad and Ben will present error and convergence plots in their reports for classical integrator. They will read Dutt et al. (2000) and try to implement it. 
\end{shaded}


\end{document}